---
title: "food_analysis1"
author: "Erica Griffin"
date: "2025-01-22"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Analysis to be conducted: 
#### All long-term data from KL/SU and AG/LL/JO to assess impacts of food (previous year tree cones, feeder bucket access) on co-variance between litter size and offspring growth. Fixed effects include access to bucket (yes or no), conestm-1, local density, female age, female age^2, local density x conestm1, local density x bucket access. Random effects: Grid/Year/Female/Litter. 

```{r prep}
library(lme4)
litter <- read.csv("~/University of Michigan Dropbox/Erica Griffin/Erica Griffin - shared folder/W25 social cue analysis/social-cues-KRSP/AnalysisData/litter_analysis.csv")
```

First, I want to start by running models that assess offspring growth and litter size independetly of each other, rather than looking at the covariance between the two. 

```{r growth}
growth_model <- lmer(std_Growt ~ 
              bucket + cones_tm1 + spr_density + age + I(age^2) + 
              spr_density*cones_tm1 + spr_density*bucket + 
              (1 | grid) + (1 | year) + (1 | squirrel_id), 
             data = litter)
summary(growth_model)
```

```{r size}
size_model <- lmer(std_LS ~ 
                bucket + cones_tm1 + spr_density + age + I(age^2) + 
                spr_density*cones_tm1 + spr_density*bucket + 
                (1 | grid) + (1 | year) + (1 | squirrel_id), # need to add in litter_id once I fix the errors 
              data = litter)
summary(size_model)
```

Now, using a  model to look at the effect on the covariance between the liter size and growth. 

```{r both}
growth_size_model <- lmer(
  std_Growt ~ 
    bucket * std_LS + cones_tm1 * std_LS +  spr_density * std_LS + 
    age * std_LS + I(age^2) * std_LS +  spr_density * cones_tm1 +  spr_density * bucket +  
    (1 | grid) +  (1 | year) +  (1 | squirrel_id), 
  data = litter)

summary(growth_size_model)
```



