---
title: "food_analysis1"
author: "Erica Griffin"
date: "2025-01-22"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Analysis to be conducted: 
#### All long-term data from KL/SU and AG/LL/JO to assess impacts of food (previous year tree cones, feeder bucket access) on co-variance between litter size and offspring growth. Fixed effects include access to bucket (yes or no), conestm-1, local density, female age, female age^2, local density x conestm1, local density x bucket access. Random effects: Grid/Year/Female/Litter. 

```{r prep}
library(nlme)
library(lme4)
litter <- read.csv("~/University of Michigan Dropbox/Erica Griffin/Erica Griffin - shared folder/W25 social cue analysis/social-cues-KRSP/AnalysisData/litter_analysis_cov.csv")
```


Here, I use the variable I calculated that is the co-variance between each of the variables for each observation: 

```{r modelboth}
cov_model <- lmer(covariance ~ 
    bucket + cones_tm1 + spr_density + age + I(age^2) +
    spr_density * cones_tm1 + spr_density * bucket + scaled_part_date + 
                (1 | grid) + (1 | year) + (1 | squirrel_id), data = litter
)
summary(cov_model)
```


