---
title: "rattle_analysis"
author: "Erica Griffin"
date: "2025-04-03"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(dplyr)
library(nlme)
library(lme4)
litter_2 <- read.csv("~/University of Michigan Dropbox/Erica Griffin/Erica Griffin - shared folder/W25 social cue analysis/social-cues-KRSP/AnalysisData/litter_analysis_cov.csv")

#Date prep: 
## create new variable detailing whether or not playbacks were heard (JO vs BT, KL, SU) - ask Ben what to do with LL, CH, and AG 
litter_playback <- litter_2 %>%
  mutate(playback = case_when(
    grid == "JO" ~ "Y", 
    grid %in% c("BT", "KL", "SU", "LL", "CH", "AG") ~ "N",  
    TRUE ~ NA_character_))
```

## Analysis to be conducted: 
1.	2018-2020 data from JO (rattle playbacks) vs. controls (BT, KL, SU) to assess social cues of density on co-variance between litter size and offspring growth. Fixed effects include conestm-1, local density, playbacks heard, female age, female age^2, grid, local density x conestm1, playbacks heard x conestm1. Random effects: Grid/Year/Female/Litter. Not including part date as it is inconsistently available.


```{r}
model2 <- lmer(covariance ~ cones_tm1 + spr_density + playback + age + I(age^2) + 
    spr_density * cones_tm1 + playback * cones_tm1 + scaled_part_date + 
                (1 | grid) + (1 | year) + (1 | squirrel_id), 
    data = litter_playback)
summary(model2)
```


