---
title: "SBN-analysis"
author: "Erica Griffin"
date: "2025-04-04"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(dplyr)
library(nlme)
library(MASS)
install.packages("lmerTest")
library(lmerTest)
library(ggplot2)
# create new variable for mast vs non-mast years 
cort <- read.csv("~/University of Michigan Dropbox/Erica Griffin/Erica Griffin - shared folder/W25 social cue analysis/social-cues-KRSP/SBNData/cort_analysis.csv")
cort <- cort %>%
  mutate(mast = if_else(year %in% c(2022, 2019, 2014, 2010, 2005, 1998, 1993), "y", "n"))
```

## Analysis to be run: First – what is the actual co-variance between offspring growth and number?, Does it differ between mast / non-mast?, What about density conditions?

```{r}
# base co-variance
base_cov <- cov(cort$std_Growt, cort$std_LS)
print(base_cov)
base_matrix <- cov(cort[, c("std_Growt", "std_LS")])
# mast co-variance 
mast <- subset(cort, mast == "y")
mast_cov <- cov(mast$std_Growt, mast$std_LS)
print(mast_cov)
# non-mast co-variance 
mast_no <- subset(cort, mast == "n")
mast_no_cov <- cov(mast_no$std_Growt, mast_no$std_LS)
print(mast_no_cov)
## First looking at spring density
summary(cort$spr_density) # mean is 2.3, with a min of 0.52 and a max of 4.7 - think that everything below the mean will be low density, and everything above will be high?

# high density co-variance 
high_dens <- subset(cort, spr_density > 2.3)
high_cov <- cov(high_dens$std_Growt, high_dens$std_LS)
print(high_cov)
# low density co-variance 
low_dens <- subset(cort, spr_density < 2.3)
low_cov <- cov(low_dens$std_Growt, low_dens$std_LS)
print(low_cov)
```

```{r}
library(ggplot2)
library(dplyr)
library(RColorBrewer)

# Calculate covariance for each group
cov_overall <- cov(cort$std_Growt, cort$std_LS)
cov_mast <- cov(subset(cort, mast == "y")$std_Growt, subset(cort, mast == "y")$std_LS)
cov_non_mast <- cov(subset(cort, mast == "n")$std_Growt, subset(cort, mast == "n")$std_LS)
cov_high_density <- cov(subset(cort, spr_density > 2.3)$std_Growt, subset(cort, spr_density > 2.3)$std_LS)
cov_low_density <- cov(subset(cort, spr_density < 2.3)$std_Growt, subset(cort, spr_density < 2.3)$std_LS)

# Create a data frame for the covariances
cov_values <- data.frame(
  Group = c("Overall", "Mast", "Non-Mast"),
  Covariance = c(cov_overall, cov_mast, cov_non_mast)
)

# Add a grouping variable to the original data
cort_grouped <- cort %>%
  mutate(Group = case_when(
    mast == "y" ~ "Mast",
    mast == "n" ~ "Non-Mast",
    TRUE ~ "Other"
  ))

# For simplicity, add 'Overall' as a duplicate of the whole dataset
cort_all <- cort %>%
  mutate(Group = "Overall")

# Combine all data
cort_combined <- bind_rows(cort_all, cort_grouped)

# Define color palette for colorblind-friendly options (Set1 is colorblind-friendly)
cb_palette <- c("#E69F00", "#56B4E9", "#009E73")  # Adding green (#009E73) as the third color

# Plot with facets and annotations for covariance values
ggplot(cort_combined, aes(x = std_Growt, y = std_LS, color = Group)) +
  geom_point(alpha = 0.7) +  # Scatter plot points
  facet_wrap(~ Group) +
  scale_color_manual(values = cb_palette) + 
    geom_smooth(method = "lm", se = FALSE, color = "black", linetype = "solid") +  # Trend lines
# Apply color palette
  labs(title = "Scatter Plots of std_Growt vs. std_LS by Group",
       x = "Standardized Growth",
       y = "Standardized Litter Size") +
  theme_minimal() +
  # Annotate covariance on each plot
  geom_text(data = cov_values, aes(x = Inf, y = Inf, label = paste("Covariance: ", round(Covariance, 2))),
            hjust = 1.1, vjust = 1.1, size = 4, inherit.aes = FALSE)

```

```{r}
library(ggplot2)
library(dplyr)
library(RColorBrewer)

# Create a new grouping for 'mast' to color points differently
cort_grouped <- cort %>%
  mutate(Mast_Group = ifelse(mast == "y", "Mast", "Non-Mast"))

# Define color palette for colorblind-friendly options (Set1 is colorblind-friendly)
cb_palette <- c("#E69F00", "#56B4E9")  # Color Universal Design (CUD) colors (Mast, Non-Mast)

# Plot all data on one graph with color-coded points based on 'mast'
ggplot(cort_grouped, aes(x = std_Growt, y = std_LS, color = Mast_Group)) +
  geom_point(alpha = 0.7) +  # Scatter plot points
  geom_smooth(aes(color = Mast_Group), method = "lm", se = FALSE, linetype = "solid") +  # Trend lines for each group
  scale_color_manual(values = cb_palette) +  # Apply color palette
  labs(title = "Scatter Plot of std_Growt vs. std_LS by Mast/Non-Mast",
       x = "Standardized Growth",
       y = "Standardized Litter Size") +
  theme_minimal() +
  theme(legend.title = element_blank())
```
## Analysis to be run: Are GCs one mechanism within which moms are minimizing this trade-off?, Looking at how fecal cort changes this variance, Is this mediated by density?


### First with int model 
```{r}
cort1 <- lmer(std_Growt ~ 
              pre_cort*std_LS + lac_cort*std_LS + age + I(age^2) + 
              (1 | grid) + (1 | year) , 
             data = cort)
summary(cort1)
```
### add density / food ? 
```{r}
```

### Next using covariance value

```{r}
cort2 <- lmer(covariance ~ 
              pre_cort + lac_cort + age + I(age^2) + 
              (1 | grid) + (1 | year) , 
             data = cort)
summary(cort2)
```



